\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{array}

\begin{document}

\section*{GeoTop Formalization Report for Sections 3 and 4}

Date: 2026-06-02.

Sections 3 and 4 of \texttt{geotop.tex} are not yet sorry-free. They are
isolated in a cached development stack, and the current active section session
has a successful warm-cache build.

Evidence checked locally:
\begin{itemize}
\item A fetch of colleague \texttt{main} over HTTPS reached \texttt{81d9ff22}
(\texttt{Export TFF problems for Top0 topology sessions}). The relevant faster
theorem-index generator commit, \texttt{0284ba9c}
(\texttt{Speed up theorem index generation}), is already contained in the local
branch.
\item The fast \texttt{gen\_index.sh} implementation is the Python single-pass
version and still includes the local Section 3--4 theory stack. The refreshed
theorem index ran in about half a second, while \texttt{gen\_stmt\_index.sh}
ran in about two seconds.
\item A warm-cache section build passed:
\texttt{/project/bin/isabelle build -d . -d dev34\_pre -d dev34\_prefix -d dev34\_facts -d dev34\_workfacts -d dev34\_linkfacts -d dev34\_graphfacts -d dev34\_graphwork -d dev34\_openstar -d dev34 GeoTop34Dev},
with the outer command reporting \texttt{0:00:33 elapsed time}.
\item The current committed branch tip before this report refresh is
\texttt{6e6a0f25} (\texttt{Prove GeoTop probe triangle containment}).
\item Excluding the intentionally dirty \texttt{dev34\_pre/GeoTop.thy} mirror,
the target section-specific theories currently contain 21 executable
\texttt{sorry}s: 10 in \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy} and 11 in
\texttt{dev34/GeoTop\_3\_4.thy}.
\end{itemize}

The practical consequence is that Sections 3 and 4 have a working, green
development session with a much smaller local target surface than the original
monolithic script. Completion still requires eliminating the listed proof
holes. The compact cone-over-compact closedness lemma is now proved, closing the
radial bad-endpoint closedness bottleneck. The major open clusters are now the
book's Figure 4.10 fan model turning a polygonal or broken-line link into a
cone-over-link subdivision, the small semicircle/small circle domain
constructions, the isolated 2-cell/Jordan contradiction, the remaining local
Theorem 4.9 converse plane-neighborhood obligations, and several larger
Section 3/early Section 4 prefix arguments. The one-sided and three-sided chart contradictions
are now narrowed to explicit domain-level obligations plus a topological image
step.

\section*{Layout}

The Section 3--4 development is split as follows:
\begin{itemize}
\item \texttt{dev34\_pre/GeoTop.thy}: dirty cached import of the original script; it still contains original later-section sketches and is excluded from the Section 3--4 target count.
\item \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}: Section 3 and early Section 4.
\item \texttt{dev34\_facts/GeoTop\_3\_4\_Facts.thy}: Jordan-curve facts and local manifold helpers.
\item \texttt{dev34\_workfacts}, \texttt{dev34\_linkfacts}, \texttt{dev34\_graphfacts}, \texttt{dev34\_graphwork}, and \texttt{dev34\_openstar}: cached support layers.
\item \texttt{dev34/GeoTop\_3\_4.thy}: active Section 4 manifold/star work and the final layer of the section-specific stack; it currently contains 11 executable \texttt{sorry}s.
\end{itemize}

\section*{Section 3 Counterparts}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.13\linewidth}
                  >{\raggedright\arraybackslash}p{0.45\linewidth}
                  >{\raggedright\arraybackslash}p{0.18\linewidth}
                  >{\raggedright\arraybackslash}p{0.16\linewidth}}
\textbf{Book item} & \textbf{Book statement, abbreviated} & \textbf{Isabelle} & \textbf{File}\\
\hline
Theorem 3.1 & Matched simplexes admit a simplicial homeomorphism carrying vertices to assigned images. & \texttt{Theorem\_GT\_3\_1} & \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}\\
Theorem 3.2 & In the equal-dimensional case, the simplex homeomorphism extends to the whole Euclidean space. & \texttt{Theorem\_GT\_3\_2} & \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}\\
Theorem 3.3 & A triangulated polygonal disk with more than one 2-simplex has a free 2-simplex. & \texttt{Theorem\_GT\_3\_3} & \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}\\
Theorem 3.4 & Every polygon is carried by a plane homeomorphism to the frontier of a 2-simplex. & \texttt{Theorem\_GT\_3\_4} & \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}\\
Theorem 3.5 & Any two polygons in \(R^2\) are equivalent by a plane homeomorphism. & \texttt{Theorem\_GT\_3\_5} & \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}\\
Theorem 3.6 & A polygon bounds a topological 2-cell. & \texttt{Theorem\_GT\_3\_6} & \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}\\
Theorem 3.7 & The polygon-to-simplex homeomorphism can be chosen fixed outside a prescribed open neighborhood. & \texttt{Theorem\_GT\_3\_7} & \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}\\
\end{longtable}

\section*{Section 4 Counterparts}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.13\linewidth}
                  >{\raggedright\arraybackslash}p{0.45\linewidth}
                  >{\raggedright\arraybackslash}p{0.18\linewidth}
                  >{\raggedright\arraybackslash}p{0.16\linewidth}}
\textbf{Book item} & \textbf{Book statement, abbreviated} & \textbf{Isabelle} & \textbf{File}\\
\hline
Theorem 4.1 & Distinct components of an open Euclidean set are separated by disjoint open subsets. & \texttt{Theorem\_GT\_4\_1} & \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}\\
Theorem 4.2 & An arc across a polygonal disk separates the polygon interior into two expected open sides. & \texttt{Theorem\_GT\_4\_2} & \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}\\
Theorem 4.3 & A topological 1-sphere in \(R^2\) separates the plane. & \texttt{Theorem\_GT\_4\_3} & \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}\\
Theorem 4.4 & Two disjoint arcs from opposite boundary points leave \(Q\) and \(S\) in the frontier of the same component. & \texttt{Theorem\_GT\_4\_4} & \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy}\\
Theorem 4.5 & No arc separates \(R^2\). & \texttt{Theorem\_GT\_4\_5} & \texttt{dev34\_facts/GeoTop\_3\_4\_Facts.thy}\\
Theorem 4.6 & For a 1-sphere \(J\) and component \(U\) of \(R^2-J\), \(\operatorname{Fr} U=J\). & \texttt{Theorem\_GT\_4\_6} & \texttt{dev34\_facts/GeoTop\_3\_4\_Facts.thy}\\
Theorem 4.7 & A 1-sphere in \(R^2\) has exactly one bounded complement component. & \texttt{Theorem\_GT\_4\_7} & \texttt{dev34\_facts/GeoTop\_3\_4\_Facts.thy}\\
Theorem 4.8 & If \(|K|\) is a 2-manifold, every vertex star of \(K\) is a combinatorial 2-cell. & \texttt{Theorem\_GT\_4\_8} & \texttt{dev34/GeoTop\_3\_4.thy}\\
Theorem 4.9 & If \(|K|\) is a 2-manifold with boundary, vertex stars are combinatorial 2-cells and the boundary is the union of one-triangle edges. & \texttt{Theorem\_GT\_4\_9} & \texttt{dev34/GeoTop\_3\_4.thy}\\
Theorem 4.10 & For a closed 2-manifold with boundary in \(R^2\), manifold boundary equals topological frontier. & \texttt{Theorem\_GT\_4\_10} & \texttt{dev34/GeoTop\_3\_4.thy}\\
\end{longtable}

\section*{Open Proof Holes}

The current holes in \texttt{dev34\_prefix/GeoTop\_3\_4\_Prefix.thy} are:
\begin{itemize}
\item \texttt{Theorem\_GT\_3\_3}: induction/strong free-simplex claim at line 844.
\item \texttt{Theorem\_GT\_3\_4}: base case and induction step for reducing a polygonal disk to one 2-simplex at lines 892 and 905.
\item \texttt{Theorem\_GT\_3\_7}: supported polygon-to-simplex homeomorphism, fixed outside the prescribed open neighborhood, at line 1362.
\item \texttt{Theorem\_GT\_4\_2}: final arc-separation disjointness/decomposition step at line 1715.
\item \texttt{Theorem\_GT\_4\_4}: brick-decomposition and frontier-component construction steps at lines 1810, 1818, 1828, 1839, and 1849.
\end{itemize}

The current holes in \texttt{dev34/GeoTop\_3\_4.thy} are:
\begin{itemize}
\item \texttt{geotop\_vertex\_star\_standard\_fan\_isomorphism\_from\_finite\_linear\_link\_line\_or\_polygon\_dev34} at line 3201.
\item \texttt{geotop\_unique\_incident\_2simplex\_small\_semicircle\_domain\_separates\_chart\_dev34} at line 4001.
\item \texttt{geotop\_three\_incident\_2simplex\_small\_circle\_domain\_not\_separates\_chart\_dev34} at line 4061.
\item \texttt{geotop\_2cell\_chart\_1sphere\_complement\_not\_connected\_dev34} at line 4197.
\item \texttt{geotop\_shared\_edge\_probe\_diamond\_contains\_ball\_dev34}, the newly isolated local-diamond ball-containment proof sketch, at lines 7973, 7976, 7982, 7987, and 7992.
\item \texttt{geotop\_2simplex\_opposite\_side\_shared\_edge\_rel\_interior\_subset\_HOL\_interior\_union\_dev34} at line 8063; this is the remaining analytic local-neighborhood step for the same-complex two-triangle shared-edge local disk model.
\item \texttt{geotop\_polygon\_link\_vertex\_is\_HOL\_interior\_polyhedron\_dev34} at line 8419; this is the Figure 4.10 full-disk vertex-star local Euclidean-neighborhood branch of Theorem 4.9's boundary converse.
\end{itemize}

\section*{Recent Progress and Supporting Material}

The active file now proves most of the radial and local connected-neighborhood
infrastructure used in Moise's Lemma 5 route. Important helpers include
\texttt{geotop\_punctured\_star\_separation\_side\_meets\_vertex\_neighborhood\_dev34},
\texttt{geotop\_2\_manifold\_open\_subset\_connected\_punctured\_neighborhood\_dev34},
\texttt{geotop\_2\_manifold\_with\_boundary\_open\_subset\_connected\_punctured\_neighborhood\_dev34},
\texttt{geotop\_2\_manifold\_vertex\_star\_punctured\_connected\_dev34},
\texttt{geotop\_2\_manifold\_with\_boundary\_vertex\_star\_punctured\_connected\_dev34},
\texttt{geotop\_punctured\_star\_radial\_endpoint\_choice\_property\_dev34},
\texttt{geotop\_radial\_endpoint\_choice\_preimage\_eq\_cone\_dev34},
\texttt{geotop\_punctured\_star\_radial\_endpoint\_projection\_dev34}, and
\texttt{geotop\_link\_open\_radial\_cone\_open\_in\_punctured\_star\_dev34}.

Since the previous report, radial cone openness has been reduced through a
simplex-local endpoint-control statement. The current branch proves
\texttt{geotop\_subspace\_open\_from\_euclidean\_ball\_witness\_dev34},
\texttt{geotop\_complex\_point\_finite\_local\_carrier\_dev34},
\texttt{geotop\_finite\_carrier\_local\_ball\_glue\_dev34},
\texttt{geotop\_finite\_local\_carrier\_radial\_cone\_point\_neighborhood\_dev34},
\texttt{geotop\_euclidean\_open\_radial\_cone\_point\_neighborhood\_dev34},
\texttt{geotop\_euclidean\_open\_radial\_cone\_open\_in\_punctured\_star\_dev34},
\texttt{geotop\_simplex\_point\_neighborhood\_empty\_if\_notin\_dev34},
\texttt{geotop\_radial\_cone\_simplex\_point\_neighborhood\_at\_member\_dev34},
\texttt{geotop\_radial\_endpoint\_simplex\_local\_ball\_control\_dev34},
\texttt{geotop\_ball\_avoids\_closed\_not\_containing\_allow\_empty\_dev34},
\texttt{geotop\_radial\_cone\_over\_compact\_closed\_dev34},
\texttt{geotop\_radial\_bad\_endpoint\_cone\_avoids\_point\_dev34}, and
\texttt{geotop\_radial\_bad\_endpoint\_cone\_closed\_dev34}.
The compact cone-over-compact helper proves the general closedness of the image
of \(\{0..1\}\times C\) under the affine cone map
\((s,y)\mapsto (1-s)v+s y\), assuming \(C\) compact, by reducing to compactness
of a continuous image.

The chart-local Section 4 statements have also been audited against the book
argument. The one-sided and three-sided chart contradictions now first extract
a relative metric ball from the local chart neighborhood and then delegate to
explicit small semicircle/small circle domain construction lemmas and an
isolated 2-cell/Jordan contradiction. Since the previous report, the
image-side wrappers have been proved from these narrower obligations using
\texttt{top1\_homeomorphism\_on\_subspace\_image\_dev34},
\texttt{geotop\_homeomorphism\_image\_arc\_dev34}, and
\texttt{geotop\_homeomorphism\_image\_1sphere\_dev34}. The cone-over-link
bridge for Theorem 4.8 has likewise been narrowed. The link-complex wrapper now
proves the finite linear-graph hypotheses and delegates the remaining
Figure 4.10 construction to
\texttt{geotop\_vertex\_star\_standard\_fan\_isomorphism\_from\_finite\_linear\_link\_line\_or\_polygon\_dev34}.

Since the previous report, the boundary-equality half of Theorem 4.9 has been
split further. The broad subset helper now proves its contradiction argument
from a carrier split, and the remaining content is named as local chart
obligations: two distinct 2-simplexes of the same complex sharing an edge form
an ordinary Euclidean neighborhood along the edge interior, and a polygonal link
gives a full disk-star Euclidean neighborhood at the vertex. The two-sided
vertex-link branch is now proved: exact two-face incidence gives degree two at
every link vertex, connectedness from Lemma 5 makes the link a single
component, and the finite connected degree-two linear graph classifier turns
that component into a polygon. New proved helpers include
\texttt{geotop\_link\_vertices\_face\_count\_two\_incident\_link\_edge\_card\_dev34},
\texttt{geotop\_link\_component\_preserves\_incident\_edge\_card\_two\_dev34},
and \texttt{geotop\_link\_component\_degree\_two\_polygon\_witness\_dev34}.
The same-complex two-triangle local model has also gained the proved
face-lattice helper
\texttt{geotop\_2simplex\_face\_containing\_edge\_eq\_edge\_or\_simplex\_dev34}:
in a 2-simplex, a face containing an edge is either that edge or the full
simplex. Using it with \texttt{geotop\_is\_complex\_intersection} now proves
\texttt{geotop\_complex\_two\_2simplex\_shared\_edge\_inter\_eq\_edge\_dev34},
the exact intersection statement for distinct same-complex 2-simplexes sharing
an edge. The next vertex-form step is also proved:
\texttt{geotop\_two\_2simplex\_shared\_edge\_vertices\_obtain\_dev34}
extracts common edge vertices \texttt{a,b} and distinct opposite vertices
\texttt{c,d} for the two 2-simplexes. The affine prerequisite
\texttt{geotop\_2simplex\_opposite\_vertex\_notin\_edge\_affine\_hull\_dev34}
is now proved: the vertex opposite an edge in a 2-simplex is not on the affine
line of that edge. The combined witness
\texttt{geotop\_two\_2simplex\_shared\_edge\_vertices\_affine\_obtain\_dev34}
now packages both opposite vertices with their affine-line exclusions for the
next two-sided local-model step. The edge-line normal-form helper
\texttt{geotop\_edge\_vertices\_affine\_hull\_normal\_form\_dev34}
expresses the affine hull of the shared edge as
\(\{x.\ n\bullet x=d\}\) with \(n\neq 0\). The normal-coordinate wrapper
\texttt{geotop\_two\_2simplex\_shared\_edge\_vertices\_normal\_obtain\_dev34}
packages this line equation with the facts \(n\bullet c\neq r\) and
\(n\bullet d\neq r\) for the two opposite vertices. The helper
\texttt{geotop\_2simplex\_vertices\_HOL\_interior\_explicit\_dev34}
translates a nondegenerate GeoTop 2-simplex vertex triple into HOL's
positive-barycentric description of triangle interior, and
\texttt{geotop\_2simplex\_positive\_bary\_in\_HOL\_interior\_dev34}
provides the direct membership form of that characterization. The new
half-plane helpers
\texttt{geotop\_2simplex\_HOL\_interior\_positive\_side\_of\_edge\_line\_dev34}
and
\texttt{geotop\_2simplex\_HOL\_interior\_negative\_side\_of\_edge\_line\_dev34}
show that triangle interior points lie on the same strict side of the shared
edge line as the opposite vertex. The subset wrappers
\texttt{geotop\_2simplex\_HOL\_interior\_subset\_positive\_side\_of\_edge\_line\_dev34}
and
\texttt{geotop\_2simplex\_HOL\_interior\_subset\_negative\_side\_of\_edge\_line\_dev34}
package these pointwise facts as half-plane containments. The combined helper
\texttt{geotop\_two\_2simplex\_shared\_edge\_vertices\_side\_obtain\_dev34}
now bundles the shared-edge normal witness with the corresponding conditional
side containments for both incident 2-simplexes. The edge-line containment
helpers \texttt{geotop\_edge\_vertices\_subset\_affine\_hull\_dev34} and
\texttt{geotop\_edge\_vertices\_subset\_normal\_line\_dev34} record that the
common edge itself lies on that normal-form line. The ordinary-interior
wrappers \texttt{geotop\_2simplex\_HOL\_interior\_eq\_rel\_interior\_dev34}
and
\texttt{geotop\_complex\_distinct\_2simplex\_HOL\_interiors\_disjoint\_dev34}
convert the standard complex relative-interior disjointness fact into the
HOL-interior form needed for the same-side contradiction. The coordinate
helpers \texttt{geotop\_2simplex\_vertices\_affine\_hull\_UNIV\_dev34} and
\texttt{geotop\_2simplex\_vertices\_affine\_coordinates\_dev34} show that the
first triangle's vertices span the plane and give affine coordinates for
arbitrary points, setting up the same-side overlap construction. The
sign-coordinate helpers
\texttt{geotop\_2simplex\_positive\_side\_affine\_coordinate\_positive\_dev34}
and
\texttt{geotop\_2simplex\_negative\_side\_affine\_coordinate\_positive\_dev34}
prove that a same-side opposite vertex has positive affine coordinate at the
first triangle's opposite vertex. The real helper
\texttt{geotop\_real\_positive\_overlap\_parameter\_dev34} chooses the small
positive parameter needed to keep both triangle-interior barycentric coordinate
systems strictly positive in the overlap construction. The construction itself
is now proved in
\texttt{geotop\_2simplex\_affine\_coordinate\_HOL\_interiors\_meet\_dev34}: the
small segment point lies in both HOL interiors after substituting the affine
coordinates of the second opposite vertex. The positive- and negative-side
wrappers
\texttt{geotop\_2simplex\_positive\_same\_side\_HOL\_interiors\_meet\_dev34}
and
\texttt{geotop\_2simplex\_negative\_same\_side\_HOL\_interiors\_meet\_dev34}
now expose this as a direct same-side interior-overlap contradiction for the
shared-edge local model. The same-complex package
\texttt{geotop\_complex\_two\_2simplex\_shared\_edge\_vertices\_opposite\_sides\_dev34}
is now proved: after extracting the shared-edge normal-coordinate data, complex
relative-interior disjointness rules out both same-side cases and leaves the
two opposite-side alternatives. The same-complex wrapper
\texttt{geotop\_complex\_two\_2simplex\_shared\_edge\_rel\_interior\_subset\_HOL\_interior\_union\_dev34}
is also proved from the newly isolated analytic helper
\texttt{geotop\_2simplex\_opposite\_side\_shared\_edge\_rel\_interior\_subset\_HOL\_interior\_union\_dev34};
the remaining content is exactly the book's local Euclidean ball construction
for two opposite-side triangles along their common edge. The edge-coordinate
helper \texttt{geotop\_edge\_rel\_interior\_parameter\_dev34} is now proved,
giving the open-segment parameter \texttt{0<t<1} for points of the shared edge
relative interior. The real positivity helper
\texttt{geotop\_real\_positive\_edge\_probe\_parameter\_dev34} is also proved;
it chooses a small positive probe parameter that preserves the two positive
edge barycentric coordinates while creating a positive normal-side coordinate,
which is the next ingredient for the analytic local-neighborhood step. The
normal-probe helpers
\texttt{geotop\_2simplex\_positive\_side\_edge\_normal\_probe\_in\_HOL\_interior\_dev34}
and
\texttt{geotop\_2simplex\_negative\_side\_edge\_normal\_probe\_in\_HOL\_interior\_dev34}
are now proved: from a point in the relative interior of the shared edge, a
sufficiently small move along the chosen normal direction into either strict
side lands in the HOL interior of the corresponding incident triangle. The
package helper
\texttt{geotop\_2simplex\_opposite\_side\_shared\_edge\_normal\_probes\_in\_HOL\_interiors\_dev34}
now combines these two one-sided probes for the opposite-side shared-edge
configuration. The containment helper
\texttt{geotop\_edge\_subset\_2simplex\_vertices\_dev34} is now proved,
recording that the edge spanned by two triangle vertices is contained in the
triangle. Its immediate shared-edge consequence
\texttt{geotop\_shared\_edge\_rel\_interior\_subset\_two\_2simplexes\_dev34} is
also proved, placing the common edge relative interior inside both incident
triangles. The new helper
\texttt{geotop\_edge\_rel\_interior\_small\_subsegment\_dev34} proves the
book's horizontal base step for the local diamond: every relative-interior edge
point has a small edge-direction subsegment remaining in the relative interior.
The follow-up helper
\texttt{geotop\_shared\_edge\_small\_subsegment\_in\_two\_2simplexes\_dev34}
records that this small subsegment lies in both incident triangles.
The convexity wrapper
\texttt{geotop\_convex\_hull\_three\_points\_subset\_2simplex\_dev34} is also
proved; it packages the fact that a small triangle with vertices in a simplex
is contained in that simplex. The containment package
\texttt{geotop\_shared\_edge\_probe\_triangles\_subset\_union\_dev34} now
applies this convexity wrapper to the two small probe triangles used in the
book's local diamond argument, placing their union inside the two incident
2-simplexes. The next book step has been added as a compiling
\texttt{sorry}-first proof sketch:
\texttt{geotop\_shared\_edge\_probe\_diamond\_contains\_ball\_dev34} reduces
the local diamond ball-containment lemma to five analytic subclaims, namely
orthogonal coordinate spanning, coordinate representation, small coordinate
control near the center point, and upper/lower triangle membership. The final
ball-subset bookkeeping inside that helper is already proved from those
subclaims.

Other important cached helpers include
\texttt{geotop\_complex\_vertex\_star\_neighborhood\_dev34},
\texttt{geotop\_open\_star\_open\_in\_subspace\_locally\_finite\_dev34},
\texttt{geotop\_star\_punctured\_point\_radial\_to\_link\_dev34},
\texttt{geotop\_link\_radial\_endpoint\_unique\_dev34},
\texttt{geotop\_plane\_chart\_open\_subset\_connected\_punctured\_neighborhood},
\texttt{geotop\_plane\_chart\_point\_complement\_connected},
\texttt{geotop\_plane\_chart\_arc\_complement\_connected},
\texttt{geotop\_plane\_chart\_1sphere\_complement\_not\_connected},
\texttt{geotop\_complex\_simplex\_closed},
\texttt{geotop\_complex\_simplex\_nonempty},
\texttt{geotop\_ball\_avoids\_closed\_not\_containing},
\texttt{geotop\_radial\_endpoint\_simplex\_local\_ball\_control\_dev34},
\texttt{geotop\_radial\_cone\_over\_compact\_closed\_dev34}, and
\texttt{geotop\_radial\_bad\_endpoint\_cone\_avoids\_point\_dev34}.

\section*{Notes For Future Work}

The next book-aligned bottleneck for Theorems 4.8 and 4.9 is
\texttt{geotop\_vertex\_star\_standard\_fan\_isomorphism\_from\_finite\_linear\_link\_line\_or\_polygon\_dev34}.
This is the formal Figure 4.10 step: subdivide the boundary of a 2-simplex to
match the finite polygonal or broken-line link, add one interior vertex, cone
the boundary subdivision, and obtain a simplicial isomorphism with a subdivision
of the vertex star. The local chart contradiction wrappers are proved; the next
step there is to formalize the book's small semicircle/small circle
constructions in the chart domain and the isolated 2-cell/Jordan contradiction.
The prefix
holes in Theorems 3.3, 3.4, 3.7, 4.2, and 4.4 remain larger book-level
arguments and should be attacked with the \texttt{sorry}-first skeleton
workflow from \texttt{CLAUDE.md}.

\end{document}
